\LARGE \bf WORKING TITLE: Incorporating User Feedback in Motion Planning for Manipulators

### 2014-09-30 paper2015asml.tex
added table

\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{cases}
\usepackage{xspace}
%\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

@@

\title{\LARGE \bf
Towards a Data-driven Approach to Motion Planning
}

@@

@@

\section{Approach}
\label{sec:survey}
Our approach starts with an online survey designed to get information from multiple users about how well they like robot trajectories. In this section, we will describe in detail the infrastructure used to create the trajectories and movies that were used in the survey. We will also describe the online survey procedure in detail.

\subsection{Planning System Infrastructure}

The MoveIt! benchmarking architecture~\cite{cohen2012generic} was extended with video recording capabilities to quickly generate a large number of trajectories. The MoveIt! architecture allows for the definition of environments, referred to as planning scenes, start and goal states for robots (motion planning queries). It also allows for the use of any supported planning algorithms (planners). A combination of different scenes, motion queries, and planners was used to generate robot trajectories for evalutation. We chose three distinct scenes (shown in~\ref{fig:scenes}): a kitchen ({\sc Countertop}), an industrial workbench ({\sc Industrial}) and a drawer on a table ({\sc Drawer}). Multiple queries were generated in each scene for motions of the right arm of the PR2 robot. The robot was positioned in the scenes manually and motion planning queries were constructed by hand~\ref{fig:design}. The positioning in the scenes was done with the expectation that the planning queries would not be impossible or trivial for the planning algorithms to solve.

@@

The planning algorithms that were used were RRT-Connect~\cite{kuffner2000rrt} and RRT*.  RRT*~\cite{frazzoli-RRTstar} was used with two different cost functions: \sc{PathLength} and \sc{MaxMinClearance}.The objective for \sc{PathLength} minimizes the length of the trajectory (as the sum of the euclidean distances between ends of trajectory segments). The objective for \sc{MaxMinClearance} computes uses the minimum clearance of a configuration belonging to a trajectory as the value it is trying to maximize. Both planners are implemented in the OMPL library~\ref{OMPL:2012}.

@@

The infrastructure we designed around MoveIt! allowed us to automatically generate movies of the generated trajectories using the ROS Visualizer (Rviz). We generated movies from different viewpoints to maximize the visibility of the motion to human observers reviewing it. Each participant was allowed to provide feedback no more than once for each of the trajectories generated by the survey design. We ran the survey for 103 trajectories, requesting no more than 20 ratings per trajectory. Participants are allowed to rate multiple distinct trajectories, but no more than once. The analysis of these results is presented in Section~\ref{sec:analysis}.

@@

@@

The edges $E_\text{grid}$ used in this search are the 26-connected grid of adjacent neighboring voxels. For example, some valid adjacent voxels can be computed by adding $(\Delta x,\Delta y,\Delta z)$ to the current coordinates, where $\Delta x= \Delta y= \Delta z= {\pm1,0}$. An edge only exists in this graph if the ending voxel is collision.

@@

We compared the planned workspace trajectories of the end-effectors of the robot to this canonical trajectory for each planning problem by computing the the Hausdorff distances~\cite{dubuisson1994modified}, and Dynamic Time Warping~\cite{senin2008dynamic} costs between $\xi_{\text{BFS}}$ and each of the other three.

@@

The Hausdorff distance $H_\text{AB}$ between trajectory $\xi_\text{A}$ and trajectory $\xi_\text{B}$ can be computed as follows:
\begin{equation}
\begin{aligned}
H_\text{AB} &= \max (h_{\text{AB}}, h_{\text{BA}}) \\
h_{\text{AB}} &= \max_{q_\text{A} \in \xi_\text{A}} \min_{q_\text{B} \in \xi_\text{B}} d(q_\text{A}, q_\text{B})\\
h_{\text{BA}} &= \max_{q_\text{B} \in \xi_\text{B}} \min_{q_\text{A} \in \xi_\text{A}} d(q_\text{B}, q_\text{B})\\
\end{aligned}
\end{equation}

where $q_\text{i}$ is a configuration (or in this case an end effector position) at the waypoint in trajectory $\xi_\text{i}$ and $d(q_\text{i}, q_\text{j})$ is the euclidean distance between the trajectory waypoints.

@@

\begin{equation}
\text{imh}_\text{AB} = \frac{1}{|\xi_\text{A}|} \sum_{q_\text{A} \in \xi_\text{A}} \min_{\overline{q_\text{i}q_\text{i+1}} \in \xi_\text{B}} d(q_\text{A}, \overline{q_\text{i}q_\text{i+1}})
\end{equation}

where $n(\xi)$ is the number of waypoints in the trajectory, $\overline{q_\text{i}q_\text{i+1}}$ is the i-th segment and $d(q_\text{A}, \overline{q_\text{i}q_\text{i+1}})$ is the shortest distance between the point and any point on the straight-line segment. We calculate this distance only one way, between $\xi_{\text{BFS}}$ and each of $\xi_\text{elbow}$, $\xi_\text{wrist}$, and $\xi_\text{tip}$.

@@

\todo Write about:
\begin{itemize}
\item clearance
\item smoothness
\item angular distance
\item path length
\item create question table
\item get example trajectories (without elbow path)
\item get example snapshots high-low values of features
\end{itemize}

>>>>

\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{cases}
\usepackage{xspace}
%\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{array}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

@@

\title{\LARGE \bf
WORKING TITLE: Incorporating User Feedback in Motion Planning for Manipulators
}

@@

\begin{table*}
\centering
\begin{tabular}{|c||c|c|c|c|c|c|c|}
\hline
Efficiency  & Highly inefficient& Moderately inefficient& Slightly inefficient& Neutral & Slightly efficient& Moderately efficient& Highly efficient\\
\hline
Elegance    & Highly awkward& Moderately awkward& Slightly awkward& Neutral & Slightly elegant& Moderately elegant& Highly elegant\\
\hline
Smoothness  & Highly rough& Moderately rough& Slightly rough& Neutral & Slightly smooth& Moderately smooth& Highly smooth\\
\hline
Overall     & Extremely poor& Moderately poor& Somewhat poor& Neutral & Somewhat good& Moderately good& Extremely good\\
\hline
\end{tabular}
\caption{The rating categories and the associated scale presented to the survey participant}
\label{tab:rating_scales}
\end{table*}

@@

\section{Approach}
\label{sec:survey}
Our approach starts with an online survey designed to get information from multiple users about how well they like robot trajectories. In this section, we will describe in detail the infrastructure used to create the trajectories and movies that were used in the survey and the online 
survey procedure used.

\subsection{System Infrastructure}

In order to quickly produce a large number of robot trajectories, the MoveIt benchmarking architecture~\cite{cohen2012generic} was extended with video recording capabilities. Every trajectory was generated by a combination of \emph{scenes}, \emph{queries}, and \emph{planners}. In this paper, our trajectories are planned in three distinct scenes (shown in~\ref{fig:scenes}) which the robot can interact in: a kitchen (\emph{Countertop}), an industrial workbench (\emph{Industrial}) and a drawer on a table (\emph{Drawer}).

@@

After selecting the scenes, the robot was positioned in the scenes manually and planning queries were constructed by hand to reach a requisite number of planned trajectories~\ref{fig:design}. The positioning in the scenes was done with the expectation that the planning queries would not be impossible or trivial for the planning algorithms to solve.

Finally, the planning algorithms that were used were RRT-Connect~\cite{kuffner2000rrt}, and RRT*~\cite{frazzoli-RRTstar} with two cost functions: \emph{PathLength} and \emph{MaxMinClearance}.The objective for \emph{PathLength} minimizes the length of the trajectory (as the sum of the euclidean distances between ends of trajectory segments). The objective for \emph{MaxMinClearance} computes uses the minimum clearance of a configuration belonging to a trajectory as the value it is trying to maximize.

\todo cite OMPL and optimal planning

@@

The library of trajectory videos was collected by computing plans with each of the previously discussed planners for the planning queries and scenes hand-picked from above. The plans were then recorded in simulation through RVIZ. In designing the online survey, these video recordings would be taken from multiple vantage points to maximize the visibility of the motion to the participant reviewing it.

@@

Each participant was allowed to provide feedback no more than once for each of the trajectories generated by the survey design. We ran the survey for 103 trajectories, requesting no more than 20 ratings per trajectory. Participants are allowed to rate multiple distinct trajectories, but no more than once.The analysis of these results will be done in Section~\ref{sec:analysis}.

@@

The edges $E_\text{grid}$ used in this search are the 26-connected grid of adjacent neighboring voxels. For example, some valid adjacent voxels can be computed by adding $(\Delta x,\Delta y,\Delta z)$ to the current coordinates, where $\Delta x= \Delta y= \Delta z= \{\pm1,0\}$. An edge only exists in this graph if the ending voxel is collision.

@@

We compared them by computing the the Hausdorff distances~\cite{dubuisson1994modified}, and Dynamic Time Warping~\cite{senin2008dynamic} costs between $\xi_{\text{BFS}}$ and each of the other three.

@@

The Hausdorff distance $H_\text{AB}$ between trajectory $\xi_\text{A}$ and trajectory $\xi_\text{B}$ can be computed as follows:
\begin{equation}
\begin{aligned}
H_\text{AB} &= \max (h_{\text{AB}}, h_{\text{BA}}) \\
h_{\text{AB}} &= \max_{q_\text{A} \in \xi_\text{A}} \min_{q_\text{B} \in \xi_\text{B}} \text{d}(q_\text{A}, q_\text{B})\\
h_{\text{BA}} &= \max_{q_\text{B} \in \xi_\text{B}} \min_{q_\text{A} \in \xi_\text{A}} \text{d}(q_\text{B}, q_\text{A})\\
\end{aligned}
\end{equation}

where $q_\text{A}$ is a configuration (or in this case an end effector position) at the waypoint in trajectory \tj{A} and $\text{d}(q_\text{i}, q_\text{j})$ is the euclidean distance between the trajectory waypoints.

@@

\begin{equation}
\text{imh}_\text{AB} = \frac{1}{n_A} \sum_{q_\text{A} \in \xi_\text{A}} \min_{\overline{q_\text{B,i}} \in \xi_\text{B}} \text{d}(q_\text{A}, \overline{q_\text{B,i}})
\end{equation}

where $n(\xi)$ is the number of waypoints in the trajectory, $\overline{q_\text{B,i}}$ is the i-th segment in \tj{B}, and $\text{d}(q, \overline{q})$ is the shortest distance between the point and the line segment. We calculate this distance only one way, for $(\tj{elbow},\tj{BFS})$, $(\tj{wrist},\tj{BFS})$. and $(\tj{tip},\tj{BFS})$.

@@

\todo Write about:
\begin{itemize}
\item create question table
\item get example trajectories (without elbow path)
\item get example snapshots high-low values of features
\end{itemize}
